---
title: "Zero_inflatted_model"
output: html_document
date: "2023-03-06"
---

#download packages
```{r message = FALSE}
require(ggplot2)
library(tidyverse)
library(dplyr)
require(pscl)
require(car)
require(MASS)
require(boot)
library(lattice) # alternatively can use package ZIM for zero-inflated models
library(lmtest)
library(MASS)
library(tidyverse)
library(easystats)
library(ggeffects)
library(ggplot2)
library(scales)
library(gridExtra)
library(easystats)
library(cowplot)
```

```{r}
p_a <- read_csv("data_final_DOH.csv")
p_a
```

```{r}
table(p_a$Positive_Number)
table(p_a$Negative_Number)
table(p_a$Collective_Number)
table(p_a$Individual_Number)
```


```{r message = FALSE}
p <- read_csv("DOH.csv")
```

#Change variable names 
```{r}
p1 <- 
  p %>% 
  rename(State_recode = `State_ recode`, 
        White_percent = `White_\bpercent`, 
        Risk_Factor ='RiskFactor_2_CTA', 
        Social_Disparities = 'SocialDisparities_3_CTA', 
        Debunk_MI = 'Debunk_4_CTA',
        Uncertainty_Reduction = 'UncertaintyReduction_5_CTA',  
        Testing = 'Testing_6_CTA', 
        Vaccine = 'Vaccine_7_CTA', 
        Pre_Action = 'Action_13_CTA', 
        Positive_eff = 'Positive_14a_Number', 
        Negative_eff = 'Negative_14b_Number', 
        Individual_eff = 'Individual_14c_Number', 
        Collective_eff = 'Collective_14d_Number', 
        Prosperity_ranking = 'ProspertiyRanking', 
        Minority_percent = 'minority_percent'
  ) 
```

#Transform to bi-nominal only 1 and 0 for various variables 
```{r}
p3 <- 
  p1 %>% 
mutate(Risk_Factor = ifelse(Risk_Factor %in% c('88', '888'), 0, 1)) %>% 
mutate(Social_Disparities = ifelse(Social_Disparities %in% c('88', '888'), 0, 1)) %>% 
mutate(Debunk_MI = ifelse(Debunk_MI %in% c('88', '888'), 0, 1)) %>% 
mutate(Uncertainty_Reduction = ifelse(Uncertainty_Reduction %in% c('88', '888'), 0, 1))
p3
```

```{r}
glimpse(p3)
```

```{r}
table(p3$Risk_Factor)
table(p3$Social_Disparities)
table(p3$Debunk_MI)
table(p3$Uncertainty_Reduction)
```

```{r}
table(p3$Positive_eff)
table(p3$Negative_eff)
table(p3$Collective_eff)
table(p3$Individual_eff)

```


```{r}
# Check the column names in p3
colnames(p3)

# Check the data types in p3 for relevant columns
str(p3[c("Risk_Factor", "Social_Disparities", "Debunk_MI", "Uncertainty_Reduction")])

# Modify the code to select the columns
p2 <- p3 %>%
  mutate(
    Risk_Factor = as.factor(Risk_Factor),
    Social_Disparities = as.factor(Social_Disparities),
    Debunk_MI = as.factor(Debunk_MI),
    Uncertainty_Reduction = as.factor(Uncertainty_Reduction)
  )
p2
```

```{r}
# write a csv file of the p2
write.csv(p2, file = "p2.csv", row.names = FALSE)
```



===== NEW==== 

```{r}
glimpse(p3) 
```

```{r}
colnames(p2)
```

```{r}
table(p3$Pre_Action)
```

```{r}
na_check_Risk_Factor <- any(is.na(p2$Risk_Factor))
na_check_Risk_Factor
na_check_Social_Disparities <- any(is.na(p2$Social_Disparities))
na_check_Social_Disparities 
na_check_Debunk_MI <- any(is.na(p2$Debunk_MI))
na_check_Debunk_MI
na_check_Uncertainty_Reduction <- any(is.na(p2$Uncertainty_Reduction))
na_check_Uncertainty_Reduction 
```



========
#RQ1: To what extent do the state health departments communicate about risks (i.e., uncertainty reduction, health risk factors, misinformation correction and disparities) related to COVID-19 on their Facebook accounts between January and December 2020?
```{r}
table(p2$Risk_Factor)
table(p2$Social_Disparities)
table(p2$Debunk_MI )
table(p2$Uncertainty_Reduction)
```




#RQ2:To what extent do the state health departments communicate outcome expectancies (2a)? What are the differences between the use of different types of expectancies (positive or negative and individual versus collective) on state health departments’  Facebook accounts between January and December 2020 (2b)?
```{r}
# Assuming you have two vectors: p2$Positive_eff and p2$Negative_eff
# Perform a two-sample t-test
result_t_test1 <- t.test(p2$Positive_eff, p2$Negative_eff)

# Print the results
print(result_t_test1)

```
#parameters
```{r}
model_parameters(result_t_test1)
```
# z-test "Collective_eff - Individual_eff" 
```{r}
result_t_test2 <- t.test(p2$Collective_eff, p2$Individual_eff)
result_t_test2
```
#parameters
```{r}
model_parameters(result_t_test2)
```



#RQ3:To what extent do state health departments incorporate a set of risk persuasion techniques (i.e., uncertainty reduction, health risk factors, misinformation correction and disparities) in their call-to-action regarding COVID-19 between January and December 2020?

```{r}
df <- p3 %>%
  mutate(
    Pre_Action = ifelse(Pre_Action == 0 | Pre_Action == 88, 0, 1), 
    New_Risk = ifelse(Risk_Factor + Social_Disparities + Debunk_MI + Uncertainty_Reduction == 0, 0, 1), 
    New_Eff = ifelse(Positive_eff  + Negative_eff + Individual_eff + Collective_eff == 0, 0, 1)
  ) %>%
  filter(Pre_Action == 1)
df
```


```{r}
glimpse(df)
table(df$Pre_Action)
table(df$New_Risk)
table(df$New_Eff)
```



```{r}
# Define the APA-style theme
theme_apa <- function() {
  theme_minimal() +
    theme(
      text = element_text(family = "Times New Roman", size = 10),
      plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
      axis.title = element_text(size = 12, face = "bold"),
      axis.text = element_text(size = 10),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      panel.border = element_blank(),
      panel.background = element_blank(),
      legend.position = "right",
      legend.text = element_text(size = 12), 
      axis.line = element_line(color = "black")
    )
}
```


Run Chi-Square for New_Risk

```{r}
# Create a contingency table
contingency_New_Risk <- table(df$New_Risk)
# Perform the chi-square test
chi_square_New_Risk <- chisq.test(contingency_New_Risk)
# Print the results
chi_square_New_Risk
```
```{r}
model_parameters(chi_square_New_Risk)
```

```{r}
# Create a data frame with the Chi-squared statistic and p-value
results <- data.frame(Test = "chi_square_New_Risk", Chi2 = chi_square_New_Risk$statistic, p = chi_square_New_Risk$p.value)

# Create a horizontal bar chart-like visualization
library(ggplot2)
ggplot(results, aes(x = Test, y = Chi2, fill = p < 0.001)) +
  geom_bar(stat = "identity", width = 0.5) +
  labs(title = "Chi-squared test for given probabilities",
       y = "Chi-squared statistic") +
  scale_fill_manual(values = c("TRUE" = "purple", "FALSE" = "blue")) +
  coord_flip() +
  theme_apa()
```

============ 

#RQ4: To what extent do state-level poverty, percentage of minority populations and government trifecta predict  state health departments’ risk persuasion techniques (i.e., uncertainty reduction, health risk factors, misinformation correction and disparities) (4a), outcome expectancies (4b) and call-to-action (4c) on state health departments’ Facebook accounts between January and December 2020?

```{r}
df1 <- p3 %>% 
   mutate(
    Pre_Action = ifelse(Pre_Action == 0 | Pre_Action == 88, 0, 1), 
    New_Risk = ifelse(Risk_Factor + Social_Disparities + Debunk_MI + Uncertainty_Reduction == 0, 0, 1), 
    New_Eff = ifelse(Positive_eff  + Negative_eff + Individual_eff + Collective_eff == 0, 0, 1)
  ) 
df1
```



```{r}
df1 
glimpse(df1)
```

```{r}
table(df1$Pre_Action)
table(df1$New_Risk)
table(df1$New_Eff)
```

```{r}
df2 <- df1 %>% 
   #mutate_at(vars(Pre_Action, New_Risk, New_Eff), ~ifelse(. == 0, 0, 1)) %>  
   mutate(Trifecta = as.factor(Trifecta))
df2  
```

```{r}
glimpse(df2)
table(df2$Pre_Action)
table(df2$New_Risk)
table(df2$New_Eff)
```

#CTA
```{r}
library(lmtest)
model1 <- glm(Pre_Action ~ Trifecta + Minority_percent + Poverty_percent,
              family = binomial,
              data = df2)
summary(model1)
```

```{r}
model_parameters(model1, exponentiate = TRUE)
```

# Create individual ggpredict plots and assign them to variables
plot1 <- ggpredict(M2b1_a, "Trifecta") |> plot() + theme_apa() +
  labs(title = "Predicted POE by GT",
       x = "GT",
       y = "POE") +
  scale_x_discrete(labels = c("No", "Yes"))


```{r}
# Create individual ggpredict plots and assign them to variables
plot1 <- ggpredict(model1, "Trifecta") |> plot() + theme_apa() +
  labs(title = "Predicted Call-to-action by Government Trifecta",
       x = "Government Trifecta",
       y = "Call-to-action") +
  scale_x_discrete(labels = c("No", "Yes"))

plot2 <- ggpredict(model1, "Minority_percent") |> plot() + theme_apa() +
  labs(title = "Predicted CTA by Minority Percentage",
       x = "Minority Percentage %",
       y = "Call-to-action")

plot3 <- ggpredict(model1, "Poverty_percent") |> plot() + theme_apa() +
  labs(title = "Predicted CTA by Poverty Percentage",
       x = "Poverty Percentage %",
       y = "Call-to-action")

# Create the combined plot
combined_plot1 <- plot1/(plot2 + plot3)

# Print the combined plot
print(combined_plot1)

# Save the combined boxplot as a PNG file
ggsave("New_SED_CTA.png", plot = combined_plot1, width = 8, height = 4, units = "in")
```


#Risk

```{r}
model2<- glm(New_Risk ~ Trifecta + Minority_percent + Poverty_percent,
                 family = binomial,
                 data = df2)
summary(model2)
```

```{r}
model_parameters(model2,  exponentiate = TRUE)
```

```{r}
# Create individual ggpredict plots and assign them to variables
plot1 <- ggpredict(model2, "Trifecta") |> plot() + theme_apa() +
  labs(title = "Predicted Risks by Government Trifecta",
       x = "Government Trifecta",
       y = "Risks") +
  scale_x_discrete(labels = c("No", "Yes"))

plot2 <- ggpredict(model2, "Minority_percent") |> plot() + theme_apa() +
  labs(title = "Predicted Risks by Minority Percentage",
       x = "Minority Percentage %",
       y = "Risks")

plot3 <- ggpredict(model2, "Poverty_percent") |> plot() + theme_apa() +
  labs(title = "Predicted Risks by Poverty Percentage",
       x = "Poverty Percentage %",
       y = "Risks")

# Create the combined plot
combined_plot2 <- plot1/(plot2 + plot3)

# Print the combined plot
print(combined_plot2)

# Save the combined boxplot as a PNG file
ggsave("New_SED_Risks.png", plot = combined_plot2, width = 8, height = 4, units = "in")
```

#Expectancy 

```{r}
model3<- glm(New_Eff ~ Trifecta + Minority_percent + Poverty_percent + cases,
                 family = binomial,
                 data = df2)
summary(model3)
```


```{r}
model_parameters(model3,  exponentiate = TRUE)
```
```{r}
# Create individual ggpredict plots and assign them to variables
plot1 <- ggpredict(model3, "Trifecta") |> plot() + theme_apa() +
  labs(title = "Predicted Outcome Expectancy by Government Trifecta",
       x = "Government Trifecta",
       y = "Outcome Expectancy") +
  scale_x_discrete(labels = c("No", "Yes"))

plot2 <- ggpredict(model3, "Minority_percent") |> plot() + theme_apa() +
  labs(title = "Predicted Outcome Expectancy by 
       Minority Percentage",
       x = "Minority Percentage %",
       y = "Outcome Expectancy")

plot3 <- ggpredict(model3, "Poverty_percent") |> plot() + theme_apa() +
  labs(title = "Predicted Outcome Expectancy by 
       Poverty Percentage",
       x = "Poverty Percentage %",
       y = "Outcome Expectancy")

# Create the combined plot
combined_plot3 <- plot1/(plot2 + plot3)

# Print the combined plot
print(combined_plot3)

# Save the combined boxplot as a PNG file
ggsave("New_SED_Expectancy.png", plot = combined_plot3, width = 8, height = 4, units = "in")
```

===o0o===END HERE===o0o===END HERE===o0o===END HERE===o0o===END HERE===o0o===END HERE===o0o===END HERE===o0o===END HERE===o0o===END HERE===o0o===END HERE===o0o===END HERE===o0o===END HERE===o0o===END HERE===o0o===END HERE===o0o===END HERE===o0o===END HERE===o0o===END HERE===o0o===END HERE===o0o===END HERE===o0o===END HERE===o0o===END HERE===o0o===END HERE===o0o===END HERE===o0o===END HERE===o0o===END HERE===o0o===END HERE


##Prepare for modellings 

```{r}
library(ggplot2)

# Combine the four variables into one long format
p2_long <- tidyr::gather(p2, key = "Variable", value = "Value", Positive_eff, Negative_eff, Individual_eff, Collective_eff)

# Create a grouped boxplot with all four variables
ggplot(p2_long, aes(x = Variable, y = Value, fill = Variable)) +
  geom_boxplot() +
  ylab("Value") +
  ggtitle("Boxplots of Variables with Outliers") +
  theme(legend.position = "none")
```

```{r}
table(p2$Positive_eff)
table(p2$Negative_eff)
table(p2$Individual_eff)
table(p2$ Collective_eff)

```

```{r}
#cor(p2$Poverty_percent, p2$Prosperity_ranking)
#cor(p2$White_percent, p2$Minority_percent)
#cor(p2$Pre_Action, p2$Uncertainty_Reduction)
#cor(p2$Social_Disparities, p2$Risk_Factor)
```


```{r}
# Calculate the variation and mean of X
variance_Positive_eff <- var(p2$Positive_eff,  na.rm = TRUE)
mean_Positive_eff <- mean(p2$Positive_eff,  na.rm = TRUE)
print(variance_Positive_eff)
print(mean_Positive_eff)
```

```{r}

# Calculate the variation and mean of X
variance_Negative_eff <- var(p2$Negative_eff,  na.rm = TRUE)
mean_Negative_eff <- mean(p2$Negative_eff,  na.rm = TRUE)
print(variance_Negative_eff)
print(mean_Negative_eff)
```

```{r}
# Calculate the variation and mean of X
variance_Collective_eff <- var(p2$Collective_eff, na.rm = TRUE)
mean_Collective_eff <- mean(p2$Collective_eff,  na.rm = TRUE)
print(variance_Collective_eff )
print(mean_Collective_eff )
```

```{r}
# Calculate the variation and mean of X
variance_Individual_eff <- var(p2$Individual_eff,  na.rm = TRUE)
mean_Individual_eff <- mean(p2$Individual_eff,  na.rm = TRUE)
print(variance_Individual_eff )
print(mean_Individual_eff )
```


#RQ2a: To what extent risk communication effect health efficacy? 

```{r}
# Convert selected columns to numeric
p2[, c("Social_Disparities", "Risk_Factor", "Uncertainty_Reduction", "Debunk_MI")] <- 
  sapply(p2[, c("Social_Disparities", "Risk_Factor", "Uncertainty_Reduction", "Debunk_MI")], as.numeric)

# Calculate the correlation
correlation_matrix <- cor(p2[, c("Social_Disparities", "Risk_Factor", "Uncertainty_Reduction", "Debunk_MI")])

# Print the correlation matrix
print(correlation_matrix)

```

```{r}
glimpse(p2)
table(p2$Social_Disparities)
table(p2$Risk_Factor)
table(p2$Debunk_MI)
table(p2$Uncertainty_Reduction)
```

# Positive eff
```{r}
#transform variable
p2 <- na.omit(p2)
M2a <- zeroinfl(Positive_eff ~ Social_Disparities + 
                            Risk_Factor +
                            Uncertainty_Reduction +
                            Debunk_MI,
                 dist = 'poisson',
                 data = p2)
summary(M2a)
```


```{r}
#transform variable
p2 <- na.omit(p2)
M2a_1 <- zeroinfl(Positive_eff ~ Social_Disparities + 
                            Risk_Factor +
                            Uncertainty_Reduction +
                            Debunk_MI,
                 dist = 'negbin',
                 data = p2)
summary(M2a_1)
```

```{r}
missing_columns <- colnames(p2)[apply(is.na(p2), 2, any)]
missing_columns
```


```{r}
# Run the Vuong test to compare the models
vuong_testa <- vuong(M2a, M2a_1)

# View the results of the Vuong test
summary(vuong_testa)
```

#The results of the Vuong test you provided indicate a highly significant preference for "model2" over "model1." Here's the interpretation of the results:

#Raw, AIC-corrected, and BIC-corrected z-statistics: -5.756312 Alternative hypothesis (H_A): "model2 > model1" p-value: 4.2986e-09 (which is very close to zero)

#Interpretation: The p-value is extremely small (close to zero), indicating strong statistical evidence that "model2" is significantly better than "model1" in terms of its fit to the data. This suggests a clear preference for "model2" based on the test results.

#In summary, the very low p-value and negative z-statistics provide robust evidence that "model2" outperforms "model1" in explaining the data. This is a highly significant result in favor of "model2."

==> negbin use 

```{r}
model_parameters(M2a_1)
```

```{r}
# Define the APA-style theme
theme_apa <- function() {
  theme_minimal() +
    theme(
      text = element_text(family = "Times New Roman", size = 10),
      plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
      axis.title = element_text(size = 12, face = "bold"),
      axis.text = element_text(size = 10),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      panel.border = element_blank(),
      panel.background = element_blank(),
      legend.position = "right",
      legend.text = element_text(size = 12), 
      axis.line = element_line(color = "black")
    )
}
```


```{r}
# Load required libraries
library(ggplot2)
library(ggeffects)

# Create ggeffects objects for Risk_Factor and Social_Disparities
ge_risk <- ggpredict(M2a_1, terms = "Risk_Factor")
ge_social <- ggpredict(M2a_1, terms = "Social_Disparities")

# Create data frames for both boxplots
boxplot_data_risk <- data.frame(
  Group = "Risk Factors",  # Add a Group column to identify the data source
  Risk_Factor = c(0, 1),
  Predicted = ge_risk$predicted,
  CI_lower = ge_risk$conf.low,
  CI_upper = ge_risk$conf.high
)

boxplot_data_social <- data.frame(
  Group = "Social Disparities",  # Add a Group column to identify the data source
  Risk_Factor = c(0, 1),
  Predicted = ge_social$predicted,
  CI_lower = ge_social$conf.low,
  CI_upper = ge_social$conf.high
)

# Combine the data frames
combined_data <- rbind(boxplot_data_risk, boxplot_data_social)

# Create a boxplot with facets
ggplot(combined_data, aes(x = as.factor(Risk_Factor), y = Predicted)) +
  geom_boxplot() +
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper), width = 0.2, position = position_dodge(0.75)) +
  labs(title = "Predicted POE by RF and SD",
       x = "RF and SD Factors",
       y = "POE") +
  scale_x_discrete(labels = c("No", "Yes")) +
  facet_grid(. ~ Group) +  # Facet by Group (Risk Factor and Social Disparities)
  theme_apa()

# Save the combined boxplot as a PNG file
ggsave("risk_POE.png", plot = last_plot(), width = 8, height = 4, units = "in")
```


#Negative eff
```{r}
p2 <- na.omit(p2)
M2b <- zeroinfl(Negative_eff ~ Social_Disparities + 
                            Risk_Factor + 
                            Uncertainty_Reduction +
                            Debunk_MI,
                 dist = 'poisson',
                 data = p2)
summary(M2b)
```


```{r}
p2 <- na.omit(p2)
M2b_1 <- zeroinfl(Negative_eff ~ Social_Disparities + 
                            Risk_Factor + 
                            Uncertainty_Reduction +
                            Debunk_MI,
                 dist = 'negbin',
                 data = p2)
summary(M2b_1)
```

```{r}
# Run the Vuong test to compare the models
vuong_testb <- vuong(M2b, M2b_1)

# View the results of the Vuong test
summary(vuong_testb)
```

#The Vuong test results you provided indicate a preference for "model2" over "model1" but with a less significant p-value. Here's the interpretation of the results:

#Raw, AIC-corrected, and BIC-corrected z-statistics: -1.320079
#Alternative hypothesis (H_A): "model2 > model1"
#p-value: 0.093404
#Interpretation: The p-value is 0.093404, which is not extremely small but still below the conventional significance level of 0.05. This suggests that there is some evidence that "model2" might be better than "model1," but the evidence is not as strong as in cases with much smaller p-values. Therefore, the preference for "model2" is not as clear as in cases with highly significant results.

#In summary, the results suggest that there may be a preference for "model2," but the evidence is not very strong based on the p-value. The interpretation of the Vuong test results should take into consideration the specific context of your analysis and your chosen significance level.

==> poisson 


```{r}
model_parameters(M2b)
```

```{r}
# Create ggeffects objects for Risk_Factor and Social_Disparities
ge_social <- ggpredict(M2b, terms = "Social_Disparities")
ge_debunk <- ggpredict(M2b, terms = "Debunk_MI")

# Create data frames for both boxplots
boxplot_data_social <- data.frame(
  Group = "Social Disparities",  # Add a Group column to identify the data source
  Social_Disparities = c(0, 1),
  Predicted = ge_social$predicted,
  CI_lower = ge_social$conf.low,
  CI_upper = ge_social$conf.high
)

boxplot_data_debunk <- data.frame(
  Group = "Debunking Misinformation",  # Add a Group column to identify the data source
  Social_Disparities = c(0, 1),  # Ensure that the column name matches the previous data frame
  Predicted = ge_debunk$predicted,
  CI_lower = ge_debunk$conf.low,
  CI_upper = ge_debunk$conf.high
)


# Combine the data frames
combined_data1 <- rbind(boxplot_data_debunk, boxplot_data_social)

# Create a boxplot with facets
ggplot(combined_data1, aes(x = as.factor(Social_Disparities), y = Predicted)) +
  geom_boxplot() +
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper), width = 0.2, position = position_dodge(0.75)) +
  labs(title = "Predicted NOE by SD and DM",
       x = "SD and DM Factors",
       y = "NOE") +
  scale_x_discrete(labels = c("No", "Yes")) +
  facet_grid(. ~ Group) +  # Facet by Group (Risk Factor and Social Disparities)
  theme_apa()

# Save the combined boxplot as a PNG file
ggsave("risk_NOE.png", plot = last_plot(), width = 8, height = 4, units = "in")
```


#Collective eff

```{r}
p2 <- na.omit(p2)
M2c <- zeroinfl(Collective_eff ~ Social_Disparities + 
                            Risk_Factor + 
                            Uncertainty_Reduction +
                            Debunk_MI,
                 dist = 'poisson',
                 data = p2)
summary(M2c)
```

```{r}
p2 <- na.omit(p2)
M2c_1 <- zeroinfl(Collective_eff ~ Social_Disparities + 
                            Risk_Factor + 
                            Uncertainty_Reduction +
                            Debunk_MI, dist = 'geometric',
                 data = p2)
summary(M2c_1)
```

```{r}
cor(p2[, c("Social_Disparities", "Risk_Factor", "Uncertainty_Reduction", "Debunk_MI")])

```


```{r}
# Run the Vuong test to compare the models
vuong_testc <- vuong(M2c, M2c_1)

# View the results of the Vuong test
summary(vuong_testc)
```

==> geometric 

```{r}
model_parameters(M2c_1)
```

Incorporating regularization techniques like Lasso (L1 regularization) or Ridge (L2 regularization) into a zero-inflated model can help avoid overfitting and improve model performance. To apply these techniques, you would need to use specialized packages or functions that support regularized models. In R, the glmnet package is commonly used for this purpose. Here's how you can use Lasso and Ridge regression with zero-inflated models:

```{r}
library(ggeffects)
library(patchwork)
library(ggplot2)

# Create ggeffects objects for Risk_Factor and Social_Disparities
ge_risk <- ggpredict(M2c_1, terms = "Risk_Factor")
ge_social <- ggpredict(M2c_1, terms = "Social_Disparities")
ge_uncertain <- ggpredict(M2c_1, terms = "Uncertainty_Reduction")
ge_debunk <- ggpredict(M2c_1, terms = "Debunk_MI")

boxplot_data_social <- data.frame(
  Group = "SD",  # Add a Group column to identify the data source
  Risk_Factor = c(0, 1),
  Predicted = ge_social$predicted,
  CI_lower = ge_social$conf.low,
  CI_upper = ge_social$conf.high
)

# Create data frames for both boxplots
boxplot_data_risk <- data.frame(
  Group = "RF",  # Add a Group column to identify the data source
  Risk_Factor = c(0, 1),
  Predicted = ge_risk$predicted,
  CI_lower = ge_risk$conf.low,
  CI_upper = ge_risk$conf.high
)

boxplot_data_uncertain <- data.frame(
  Group = "UR",  # Add a Group column to identify the data source
  Risk_Factor = c(0, 1),
  Predicted = ge_uncertain$predicted,
  CI_lower = ge_uncertain$conf.low,
  CI_upper = ge_uncertain$conf.high
)

# Create data frames for both boxplots
boxplot_data_debunk <- data.frame(
  Group = "DM",  # Add a Group column to identify the data source
  Risk_Factor = c(0, 1),
  Predicted = ge_debunk$predicted,
  CI_lower = ge_debunk$conf.low,
  CI_upper = ge_debunk$conf.high
)

# Combine the data frames
combined_data <- rbind(boxplot_data_risk, boxplot_data_social, 
                       boxplot_data_uncertain, boxplot_data_debunk)

# Create the individual plots
plot1 <- ggplot(combined_data[combined_data$Group == "RF", ], aes(x = as.factor(Risk_Factor), y = Predicted)) +
  geom_boxplot() +
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper), width = 0.2, position = position_dodge(0.75)) +
  labs(title = "Predicted COE by RF",
       x = "RF",
       y = "COE") +
  scale_x_discrete(labels = c("0", "1")) +  # Set x-axis labels to "0" and "1"
  facet_grid(. ~ Group) +
  theme_apa()

plot2 <- ggplot(combined_data[combined_data$Group == "SD", ], aes(x = as.factor(Risk_Factor), y = Predicted)) +
  geom_boxplot() +
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper), width = 0.2, position = position_dodge(0.75)) +
  labs(title = "Predicted COE by SD",
       x = "SD",
       y = "COE") +
  scale_x_discrete(labels = c("0", "1")) +  # Set x-axis labels to "0" and "1"
  facet_grid(. ~ Group) +
  theme_apa()

plot3 <- ggplot(combined_data[combined_data$Group == "UR", ], aes(x = as.factor(Risk_Factor), y = Predicted)) +
  geom_boxplot() +
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper), width = 0.2, position = position_dodge(0.75)) +
  labs(title = "Predicted COE by UR",
       x = "UR",
       y = "COE") +
  scale_x_discrete(labels = c("0", "1")) +  # Set x-axis labels to "0" and "1"
  facet_grid(. ~ Group) +
  theme_apa()

plot4 <- ggplot(combined_data[combined_data$Group == "DM", ], aes(x = as.factor(Risk_Factor), y = Predicted)) +
  geom_boxplot() +
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper), width = 0.2, position = position_dodge(0.75)) +
  labs(title = "Predicted COE by DM",
       x = "DM",
       y = "COE") +
  scale_x_discrete(labels = c("0", "1")) +  # Set x-axis labels to "0" and "1"
  facet_grid(. ~ Group) +
  theme_apa()

# Combine the plots into a 2x2 grid layout
combined_plots <- (plot1 + plot2) / (plot3 + plot4)
combined_plots

# Save the combined plots as a PNG file
ggsave("risk_COE.png", plot = combined_plots, width = 8, height = 8, units = "in")

```


#Individual Eff 
```{r}
M2d <- zeroinfl(Individual_eff ~ Social_Disparities + 
                            Risk_Factor + 
                            Uncertainty_Reduction +
                            Debunk_MI, 
                 dist = 'poisson',
                 data = p2)
summary(M2d)
```


```{r}
M2d_1 <- zeroinfl(Individual_eff ~ Social_Disparities + 
                            Risk_Factor + 
                            Uncertainty_Reduction +
                            Debunk_MI, 
                 dist = 'geometric',
                 data = p2)
summary(M2d_1)
```

```{r}
# Run the Vuong test to compare the models
vuong_testd <- vuong(M2d, M2d_1)

# View the results of the Vuong test
summary(vuong_testd)
```

#The Vuong z-statistic results you've provided suggest strong evidence in favor of "model2" over "model1." Here's the interpretation of the results:

#Raw, AIC-corrected, and BIC-corrected z-statistics: -4.257699
#Alternative hypothesis (H_A): "model2 > model1"
#p-value: 1.0327e-05 (very close to zero)
#Interpretation: The p-value is extremely small (1.0327e-05, which is close to zero), indicating strong statistical evidence in support of the alternative hypothesis, "model2 > model1." In other words, it strongly suggests that "model2" is a significantly better model compared to "model1."

#This suggests that "model2" is the preferred model based on the Vuong test, and this preference is highly statistically significant. In practical terms, it #means that "model2" likely provides a better fit or explanation for the data compared to "model1."

==> geometric 

```{r}
model_parameters(M2d_1)
```

#Type III ANOVA 

```{r}
library(car)
Anova(M2a_1, type = 2)
Anova(M2b, type = 2)
Anova(M2c_1, type = 2)
Anova(M2d_1, type = 2)
```




#RQ2b: To what extent socio-economic factors effect health efficacy? 
```{r}
require(pscl)
require(car)
require(MASS)
require(boot)
library(lattice) # alternatively can use package ZIM for zero-inflated models
library(lmtest)
library(tidyverse)
library(cowplot)
```

```{r}
p4 <- p2 %>% 
  mutate(Trifecta = as.factor(Trifecta)) 
p4
```

#Positive_eff 
```{r}
p4 <- na.omit(p4)
M2b1 <- zeroinfl(Positive_eff ~ Trifecta + 
                            Minority_percent + 
                            Poverty_percent,
                 dist = "poisson",
                 data = p4)
summary(M2b1)
```

```{r}
p4 <- na.omit(p4)
M2b1_a <- zeroinfl(Positive_eff ~ Trifecta + 
                            Minority_percent + 
                            Poverty_percent,
                 dist = "negbin",
                 data = p4)
summary(M2b1_a)
```


```{r}
# Run the Vuong test to compare the models
vuong_test1 <- vuong(M2b1, M2b1_a)

# View the results of the Vuong test
summary(vuong_test1)
```

==> negbin 

```{r}
model_parameters(M2b1_a)
```


```{r}
library(ggeffects)
library(patchwork)
# Create individual ggpredict plots and assign them to variables
plot1 <- ggpredict(M2b1_a, "Trifecta") |> plot() + theme_apa() +
  labs(title = "Predicted POE by GT",
       x = "GT",
       y = "POE") +
  scale_x_discrete(labels = c("No", "Yes"))

plot2 <- ggpredict(M2b1_a, "Minority_percent") |> plot() + theme_apa() +
   labs(title = "Predicted POE by MP",
       x = "MP %",
       y = "POE") #+
  #scale_x_discrete(labels = c("No", "Yes"))

plot3 <- ggpredict(M2b1_a, "Poverty_percent") |> plot() + theme_apa() + 
   labs(title = "Predicted POE by PP",
       x = "PP %",
       y = "POE") 

# Create the combined plot
combined_plot3 <- plot1/(plot2 + plot3)

# Print the combined plot
print(combined_plot3)

# Save the combined boxplot as a PNG file
ggsave("SES_POE.png", plot = last_plot(), width = 8, height = 4, units = "in")

```


#Negative eff
```{r}
M2b2 <- zeroinfl(Negative_eff ~ Trifecta + 
                            Minority_percent + 
                            Poverty_percent, 
                 dist = "poisson", 
                 data = p4)
summary(M2b2)
```

```{r}
M2b2_a <- zeroinfl(Negative_eff ~ Trifecta + 
                            Minority_percent + 
                            Poverty_percent, 
                 dist = "negbin", 
                 data = p4)
summary(M2b2_a)
```


```{r}
M2b2_b <- zeroinfl(Negative_eff ~ Trifecta + 
                            Minority_percent + 
                            Poverty_percent, 
                 dist = "geometric", 
                 data = p4)
summary(M2b2_b)
```



```{r}
# Run the Vuong test to compare the models
vuong_test2 <- vuong(M2b2, M2b2_a)
vuong_test2_a <- vuong(M2b2_a, M2b2_b)
vuong_test2_b <- vuong(M2b2, M2b2_b)

# View the results of the Vuong test
#summary(vuong_test2)
```

==> negbin

```{r}
model_parameters(M2b2_a)
```

```{r}
library(ggeffects)
library(patchwork)
# Create individual ggpredict plots and assign them to variable

plot2 <- ggpredict(M2b2_a, "Minority_percent") |> plot() + theme_apa() +
   labs(title = "Predicted NOE by MP",
       x = "MP %",
       y = "POE") #+
  #scale_x_discrete(labels = c("No", "Yes"))

plot3 <- ggpredict(M2b2_a, "Poverty_percent") |> plot() + theme_apa() + 
   labs(title = "Predicted NOE by PP",
       x = "PP %",
       y = "POE") 

# Create the combined plot
combined_plot<- plot2/plot3

# Print the combined plot
print(combined_plot)

# Save the combined boxplot as a PNG file
ggsave("SES_NOE.png", plot = last_plot(), width = 8, height = 4, units = "in")
```

#Collective eff
```{r}
M2b3 <- zeroinfl(Collective_eff ~ Trifecta + 
                            Minority_percent + 
                            Poverty_percent, 
                 dist = 'poisson',
                 data = p4)
summary(M2b3)
```


```{r}
M2b3_1 <- zeroinfl(Collective_eff ~ Trifecta + 
                            Minority_percent + 
                            Poverty_percent, 
                 dist = 'negbin',
                 data = p4)
summary(M2b3_1)
```


```{r}
vuong_test2 <- vuong(M2b3, M2b3_1)
```

==> negbin

```{r}
model_parameters(M2b3_1)
```
```{r}
# Create individual ggpredict plots and assign them to variables
plot1 <- ggpredict(M2b3, "Trifecta") |> plot() + theme_apa() +
  labs(title = "Predicted COE by GT",
       x = "GT",
       y = "COE")

plot2 <- ggpredict(M2b3, "Minority_percent") |> plot() + theme_apa() +
  labs(title = "Predicted COE by MP",
       x = "MP %",
       y = "COE")

combined_plot5 <- plot_grid(plot1, 
                            plot2,
                            ncol = 1)

# Print the combined plot
print(combined_plot5)

# Save the combined boxplot as a PNG file
ggsave("SES_COE.png", plot = combined_plot5, width = 8, height = 4, units = "in")
```


#Individual Eff 
```{r}
M2b4 <- zeroinfl(Individual_eff ~ Trifecta + 
                            Minority_percent + 
                            Poverty_percent, 
                 dist = 'poisson',
                 data = p4)
summary(M2b4)
```

```{r}
M2b4_a <- zeroinfl(Individual_eff ~ Trifecta + 
                            Minority_percent + 
                            Poverty_percent, 
                 dist = 'geometric',
                 data = p4)
summary(M2b4_a)
```

```{r}
# Run the Vuong test to compare the models
vuong_test4 <- vuong(M2b4, M2b4_a)
```

==> geometric 

```{r}
model_parameters(M2b4_a)
```

```{r}
# Create individual ggpredict plots and assign them to variables
plot1 <- ggpredict(M2b4_a, "Trifecta") |> plot() + theme_apa() +
  labs(title = "Predicted IOE by GT",
       x = "GT",
       y = "IOE")
plot2 <- ggpredict(M2b4_a, "Minority_percent") |> plot() + theme_apa() +
  labs(title = "Predicted IOE by MP",
       x = "MP %",
       y = "IOE")

plot3 <- ggpredict(M2b4_a, "Poverty_percent") |> plot() + theme_apa() +
  labs(title = "Predicted IOE by PP",
       x = "PP %",
       y = "IOE")

# Create the combined plot
combined_plot6 <- plot1/(plot2 + plot3)

# Print the combined plot
print(combined_plot6)

# Save the combined boxplot as a PNG file
ggsave("SES_IOE.png", plot = combined_plot6, width = 8, height = 4, units = "in")
```

```{r}
library(car)
Anova(M2b1_a, type = 2)
Anova(M2b2_a, type = 2)
Anova(M2b3_1, type = 2)
Anova(M2b4_a, type = 2)
```

# Question 3: How CTA is predicted by risk factors and socio-economic factors



#LOGISTIC 
 Convert pre_Action to a binary variable
```{r}
library(tidyverse)
p2b <- p2 %>% 
  mutate(Pre_Action1 = case_when(
    Pre_Action == '0' ~ 0,
    Pre_Action %in% c('1', '10', '11', '12', '13', '14', '17') ~ 1,
    TRUE ~ NA_real_
  ))
p2b
```

#risk factors 
```{r}
model1 <- glm(Pre_Action1 ~ Risk_Factor + Social_Disparities + 
                Debunk_MI + Uncertainty_Reduction, 
               data = p2b, family = binomial)
summary(model1)
```

```{r}
library(easystats)
library(ggeffects)
model_parameters(model1)
```

```{r}
# Create ggeffects objects for Risk_Factor and Social_Disparities
ge_social <- ggpredict(model1, terms = "Uncertainty_Reduction")
ge_debunk <- ggpredict(model1, terms = "Risk_Factor")

# Create data frames for both boxplots
boxplot_data_social <- data.frame(
  Group = "Uncertainty Reduction",  # Add a Group column to identify the data source
  Uncertainty_Reduction = c(0, 1),
  Predicted = ge_social$predicted,
  CI_lower = ge_social$conf.low,
  CI_upper = ge_social$conf.high
)

boxplot_data_risk <- data.frame(
  Group = "Risk_Factor",  # Add a Group column to identify the data source
  Uncertainty_Reduction = c(0, 1),  # Ensure that the column name matches the previous data frame
  Predicted = ge_debunk$predicted,
  CI_lower = ge_debunk$conf.low,
  CI_upper = ge_debunk$conf.high
)


# Combine the data frames
combined_dataz <- rbind(boxplot_data_social, boxplot_data_risk)

# Create a boxplot with facets
ggplot(combined_dataz, aes(x = as.factor(Uncertainty_Reduction ), y = Predicted)) +
  geom_boxplot() +
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper), width = 0.2, position = position_dodge(0.75)) +
  labs(title = "Predicted CTA by RF and UR",
       x = "RF and UR Factors",
       y = "CTA") +
  scale_x_discrete(labels = c("No", "Yes")) +
  facet_grid(. ~ Group) +  # Facet by Group (Risk Factor and Social Disparities)
  theme_apa()

# Save the combined boxplot as a PNG file
ggsave("CTA_risk.png", plot = last_plot(), width = 8, height = 4, units = "in")
```



#socio 
```{r}
model2 <- glm(Pre_Action1 ~ Trifecta + Minority_percent +  
                Poverty_percent , data = p2b, family = binomial)
summary(model2)
```

```{r}
library(easystats)
library(ggeffects)
model_parameters(model2)
```
```{r}
plotb1 <- ggpredict(model2, "Poverty_percent[all]") |> plot() + theme_apa() +
  labs(title = "Predicted CTA by PP",
       x = "PP %",
       y = "CTA")
plotb1

#save
ggsave("CTA_SES.png", plot = plotb1, width = 8, height = 4, units = "in")
```

==========END HERE===================END HERE===================END HERE========

