---
title: "ICA_models"
output: html_document
date: "2023-03-06"
---

#download packages
```{r message = FALSE}
require(ggplot2)
library(tidyverse)
library(dplyr)
require(car)
require(MASS)
require(boot)
library(lattice) # alternatively can use package ZIM for zero-inflated models
library(lmtest)
library(MASS)
library(tidyverse)
library(easystats)
library(ggeffects)
library(ggplot2)
library(scales)
library(gridExtra)
library(cowplot)
```


```{r message = FALSE}
p <- read_csv("DOH.csv")
p
```

```{r}
# Install and load the openxlsx package
#install.packages("openxlsx")
#library(openxlsx)

# Assuming p is your dataframe
# Replace this with your actual dataframe
# For example, p <- read.csv('your_data.csv') or p <- data.frame(...)

# Write the dataframe to an Excel file
#write.xlsx(p, file = "DOH_Final.xlsx")

```


#Change variable names 
```{r}
p1 <- 
  p %>% 
  rename(State_recode = `State_ recode`, 
        White_percent = `White_\bpercent`, 
        Risk_Factor ='RiskFactor_2_CTA', 
        Social_Disparities = 'SocialDisparities_3_CTA', 
        Debunk_MI = 'Debunk_4_CTA',
        Uncertainty_Reduction = 'UncertaintyReduction_5_CTA',  
        Testing = 'Testing_6_CTA', 
        Vaccine = 'Vaccine_7_CTA', 
        Pre_Action = 'Action_13_CTA', 
        Positive_eff = 'Positive_14a_Number', 
        Negative_eff = 'Negative_14b_Number', 
        Individual_eff = 'Individual_14c_Number', 
        Collective_eff = 'Collective_14d_Number', 
        Prosperity_ranking = 'ProspertiyRanking', 
        Minority_percent = 'minority_percent'
  ) 
```

#Frequency with 88
```{r}
# Plotting frequency distribution for each variable
for (col in names(p1)) {
  if (is.numeric(p1[[col]])) {
    plot <- ggplot(p1, aes_string(x = as.name(col))) +
      geom_bar() +
      labs(title = paste("Frequency Distribution of", col),
           x = col,
           y = "Frequency")
    print(plot)
    # Save or print the plot as needed
    # ggsave(paste("plot_", col, ".png", sep=""), plot = plot, device = "png")
  }
}
```


```{r}
p4 <- 
  p1 %>% 
  mutate_all(~ ifelse(. %in% c('88', '888', "99", "999"), 0, .))
p4

```


```{r}
table(p4$Uncertainty_Reduction)
table(p4$Testing)
table(p4$Vaccine)
```

#frequency without 88
```{r}
# Plotting frequency distribution for each variable
for (col in names(p4)) {
  if (is.numeric(p4[[col]])) {
    plot1 <- ggplot(p4, aes_string(x = as.name(col))) +
      geom_bar() +
      labs(title = paste("Frequency Distribution of", col),
           x = col,
           y = "Frequency")
    print(plot1)
    # Save or print the plot as needed
    # ggsave(paste("plot_", col, ".png", sep=""), plot = plot, device = "png")
  }
}
```


============ 
#Transform to bi-nominal only 1 and 0 for various variables 
```{r}
p3 <- 
  p1 %>% 
mutate(Risk_Factor = ifelse(Risk_Factor %in% c('88', '888'), 0, 1)) %>% 
mutate(Social_Disparities = ifelse(Social_Disparities %in% c('88', '888'), 0, 1)) %>% 
mutate(Debunk_MI = ifelse(Debunk_MI %in% c('88', '888'), 0, 1)) %>% 
mutate(Uncertainty_Reduction = ifelse(Uncertainty_Reduction %in% c('88', '888'), 0, 1))
p3
```

```{r}
glimpse(p3)
```

```{r}
table(p3$Risk_Factor)
table(p3$Social_Disparities)
table(p3$Debunk_MI)
table(p3$Uncertainty_Reduction)
```

```{r}
table(p3$Positive_eff)
table(p3$Negative_eff)
table(p3$Collective_eff)
table(p3$Individual_eff)

```


```{r}
# Check the column names in p3
colnames(p3)

# Check the data types in p3 for relevant columns
str(p3[c("Risk_Factor", "Social_Disparities", "Debunk_MI", "Uncertainty_Reduction")])

# Modify the code to select the columns
p2 <- p3 %>%
  mutate(
    Risk_Factor = as.factor(Risk_Factor),
    Social_Disparities = as.factor(Social_Disparities),
    Debunk_MI = as.factor(Debunk_MI),
    Uncertainty_Reduction = as.factor(Uncertainty_Reduction)
  )
p2
```

```{r}
# write a csv file of the p2
write.csv(p2, file = "p2.csv", row.names = FALSE)
```

===== NEW==== 

```{r}
glimpse(p3) 
```

```{r}
colnames(p2)
```

```{r}
table(p3$Pre_Action)
```

```{r}
na_check_Risk_Factor <- any(is.na(p2$Risk_Factor))
na_check_Risk_Factor
na_check_Social_Disparities <- any(is.na(p2$Social_Disparities))
na_check_Social_Disparities 
na_check_Debunk_MI <- any(is.na(p2$Debunk_MI))
na_check_Debunk_MI
na_check_Uncertainty_Reduction <- any(is.na(p2$Uncertainty_Reduction))
na_check_Uncertainty_Reduction 
```

========
#RQ1: To what extent do the state health departments communicate about risks (i.e., uncertainty reduction, health risk factors, misinformation correction and disparities) related to COVID-19 on their Facebook accounts between January and December 2020?
```{r}
table(p2$Risk_Factor)
table(p2$Social_Disparities)
table(p2$Debunk_MI )
table(p2$Uncertainty_Reduction)
```

#RQ2:To what extent do the state health departments communicate outcome expectancies (2a)? What are the differences between the use of different types of expectancies (positive or negative and individual versus collective) on state health departments’  Facebook accounts between January and December 2020 (2b)?
```{r}
# Assuming you have two vectors: p2$Positive_eff and p2$Negative_eff
# Perform a two-sample t-test
result_t_test1 <- t.test(p2$Positive_eff, p2$Negative_eff)

# Print the results
print(result_t_test1)

```
#parameters
```{r}
model_parameters(result_t_test1)
```
# z-test "Collective_eff - Individual_eff" 
```{r}
result_t_test2 <- t.test(p2$Collective_eff, p2$Individual_eff)
result_t_test2
```
#parameters
```{r}
model_parameters(result_t_test2)
```



#RQ3:To what extent do state health departments incorporate a set of risk persuasion techniques (i.e., uncertainty reduction, health risk factors, misinformation correction and disparities) in their call-to-action regarding COVID-19 between January and December 2020?

```{r}
df <- p3 %>%
  mutate(
    Pre_Action = ifelse(Pre_Action == 0 | Pre_Action == 88, 0, 1), 
    New_Risk = ifelse(Risk_Factor + Social_Disparities + Debunk_MI + Uncertainty_Reduction == 0, 0, 1), 
    New_Eff = ifelse(Positive_eff  + Negative_eff + Individual_eff + Collective_eff == 0, 0, 1)
  ) %>%
  filter(Pre_Action == 1)
df
```


```{r}
glimpse(df)
table(df$Pre_Action)
table(df$New_Risk)
table(df$New_Eff)
```



```{r}
# Define the APA-style theme
theme_apa <- function() {
  theme_minimal() +
    theme(
      text = element_text(family = "Times New Roman", size = 10),
      plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
      axis.title = element_text(size = 12, face = "bold"),
      axis.text = element_text(size = 10),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      panel.border = element_blank(),
      panel.background = element_blank(),
      legend.position = "right",
      legend.text = element_text(size = 12), 
      axis.line = element_line(color = "black")
    )
}
```


Run Chi-Square for New_Risk

```{r}
# Create a contingency table
contingency_New_Risk <- table(df$New_Risk)
# Perform the chi-square test
chi_square_New_Risk <- chisq.test(contingency_New_Risk)
# Print the results
chi_square_New_Risk
```


```{r}
model_parameters(chi_square_New_Risk)
```

```{r}
# Create a data frame with the Chi-squared statistic and p-value
results <- data.frame(Test = "chi_square_New_Risk", Chi2 = chi_square_New_Risk$statistic, p = chi_square_New_Risk$p.value)

# Create a horizontal bar chart-like visualization
library(ggplot2)
ggplot(results, aes(x = Test, y = Chi2, fill = p < 0.001)) +
  geom_bar(stat = "identity", width = 0.5) +
  labs(title = "Chi-squared test for given probabilities",
       y = "Chi-squared statistic") +
  scale_fill_manual(values = c("TRUE" = "purple", "FALSE" = "blue")) +
  coord_flip() +
  theme_apa()
```

============ 

#RQ4: To what extent do state-level poverty, percentage of minority populations and government trifecta predict  state health departments’ risk persuasion techniques (i.e., uncertainty reduction, health risk factors, misinformation correction and disparities) (4a), outcome expectancies (4b) and call-to-action (4c) on state health departments’ Facebook accounts between January and December 2020?

```{r}
df1 <- p3 %>% 
   mutate(
    Pre_Action = ifelse(Pre_Action == 0 | Pre_Action == 88, 0, 1), 
    New_Risk = ifelse(Risk_Factor + Social_Disparities + Debunk_MI + Uncertainty_Reduction == 0, 0, 1), 
    New_Eff = ifelse(Positive_eff  + Negative_eff + Individual_eff + Collective_eff == 0, 0, 1)
  ) 
df1
```



```{r}
df1 
glimpse(df1)
```

```{r}
table(df1$Pre_Action)
table(df1$New_Risk)
table(df1$New_Eff)
```

```{r}
df2 <- df1 %>% 
   #mutate_at(vars(Pre_Action, New_Risk, New_Eff), ~ifelse(. == 0, 0, 1)) %>  
   mutate(Trifecta = as.factor(Trifecta))
df2  
```

```{r}
glimpse(df2)
table(df2$Pre_Action)
table(df2$New_Risk)
table(df2$New_Eff)
```

#CTA
```{r}
library(lmtest)
model1 <- glm(Pre_Action ~ Trifecta + Minority_percent + Poverty_percent,
              family = binomial,
              data = df2)
summary(model1)
```

```{r}
model_parameters(model1, exponentiate = TRUE)
```

# Create individual ggpredict plots and assign them to variables
plot1 <- ggpredict(M2b1_a, "Trifecta") |> plot() + theme_apa() +
  labs(title = "Predicted POE by GT",
       x = "GT",
       y = "POE") +
  scale_x_discrete(labels = c("No", "Yes"))


```{r}
library(ggeffects)
library(ggplot2)
library(cowplot)


# Create individual ggpredict plots and assign them to variables
plot1 <- ggpredict(model1, "Trifecta") |> plot() + theme_apa() +
  labs(title = "Predicted Call-to-action by Government Trifecta",
       x = "Government Trifecta",
       y = "Call-to-action") +
  scale_x_discrete(labels = c("No", "Yes"))

plot2 <- ggpredict(model1, terms = "Minority_percent [all]") |> plot() + theme_apa() +
  labs(title = "Predicted CTA by Minority Percentage",
       x = "Minority Percentage %",
       y = "Call-to-action")

plot3 <- ggpredict(model1, terms = "Poverty_percent [all]") |> plot() + theme_apa() +
  labs(title = "Predicted CTA by Poverty Percentage",
       x = "Poverty Percentage %",
       y = "Call-to-action")

# Arrange the plots in a grid
combined_plot1 <- plot_grid(plot1, plot2, plot3, ncol = 1)

# Print the combined plot
print(combined_plot1)

# Save the combined boxplot as a PNG file
ggsave("New_SED_CTA.png", plot = combined_plot1, width = 8, height = 4, units = "in")
```


#Risk

```{r}
model2<- glm(New_Risk ~ Trifecta + Minority_percent + Poverty_percent,
                 family = binomial,
                 data = df2)
summary(model2)
```

```{r}
model_parameters(model2,  exponentiate = TRUE)
```

```{r}
# Create individual ggpredict plots and assign them to variables
plot1 <- ggpredict(model2, "Trifecta") |> plot() + theme_apa() +
  labs(title = "Predicted Risks by Government Trifecta",
       x = "Government Trifecta",
       y = "Risks") +
  scale_x_discrete(labels = c("No", "Yes"))

plot2 <- ggpredict(model2, terms = "Minority_percent [all]") |> plot() + theme_apa() +
  labs(title = "Predicted Risks by Minority Percentage",
       x = "Minority Percentage %",
       y = "Risks")

plot3 <- ggpredict(model2, terms = "Poverty_percent [all]") |> plot() + theme_apa() +
  labs(title = "Predicted Risks by Poverty Percentage",
       x = "Poverty Percentage %",
       y = "Risks")


# Arrange the plots in a grid
combined_plot2 <- plot_grid(plot2, plot3, ncol = 1)

# Print the combined plot
print(combined_plot2)

# Save the combined boxplot as a PNG file
ggsave("New_SED_Risks.png", plot = combined_plot2, width = 8, height = 4, units = "in")
```

#Expectancy 

```{r}
model3<- glm(New_Eff ~ Trifecta + Minority_percent + Poverty_percent,
                 family = binomial,
                 data = df2)
summary(model3)
```


```{r}
model_parameters(model3,  exponentiate = TRUE)
```
```{r}
# Create individual ggpredict plots and assign them to variables
plot1 <- ggpredict(model3, "Trifecta") |> plot() + theme_apa() +
  labs(title = "Predicted Outcome Expectancy by Government Trifecta",
       x = "Government Trifecta",
       y = "Outcome Expectancy") +
  scale_x_discrete(labels = c("No", "Yes"))

plot2 <- ggpredict(model3, terms = "Minority_percent [all]") |> plot() + theme_apa() +
  labs(title = "Predicted Outcome Expectancy by 
       Minority Percentage",
       x = "Minority Percentage %",
       y = "Outcome Expectancy")

plot3 <- ggpredict(model3, terms = "Poverty_percent [all]") |> plot() + theme_apa() +
  labs(title = "Predicted Outcome Expectancy by 
       Poverty Percentage",
       x = "Poverty Percentage %",
       y = "Outcome Expectancy")


# Arrange the plots in a grid
combined_plot3 <- plot_grid(plot1, plot2, plot3, ncol = 1)

# Print the combined plot
print(combined_plot3)

# Save the combined boxplot as a PNG file
ggsave("New_SED_Expectancy.png", plot = combined_plot3, width = 8, height = 4, units = "in")
```

===o0o===END HERE===o0o===END HERE===o0o===END HERE===o0o===END HERE===o0o===END HERE===o0o===END HERE===o0o===END HERE===o0o===END HERE===o0o===END HERE===o0o===END HERE===o0o===END HERE===o0o===END HERE===o0o===END HERE===o0o===END HERE===o0o===END HERE===o0o===END HERE===o0o===END HERE===o0o===END HERE===o0o===END HERE===o0o===END HERE===o0o===END HERE===o0o===END HERE===o0o===END HERE===o0o===END HERE===o0o===END HERE


modela <- glm(Pre_Action ~ cases,
                 family = binomial,
                 data = df2)
summary(modela)



modelb <- glm(New_Risk ~ cases,
                 family = binomial,
                 data = df2)
summary(modelb)


modelc <- glm(New_Eff ~ cases,
                 family = binomial,
                 data = df2)
summary(modelc)



